Contracts for Contracts

### 2023-05-11 paper/contract_solidity.tex
some grammar
correct understanding of negative temporal property

In this section, we introduce \lang informally with examples.
\lang is a non-breaking extension that additionally provides means
to specify behavioral contracts on top of the Solidity language. We provide
a brief introduction of Solidity first, then discuss our extension of behavioral
contracts.

@@

\begin{lstlisting}
  # ts1 @ f(x) returns z =/> ts2 @ g(a) returns c /\ side-cond
\end{lstlisting}
It enforces that when @g@ is invoked, we check that @f@ has not invoked
\emph{and} the side condition is evaluated to true.
We do not enforce that @g@ cannot be invoked eventually
after invoking @f@.

@@

>>>>

In this section, we introduce \lang informally with examples.
\lang is a non-breaking extension that additionally provides means
to specify behavioral contracts on top of the Solidity language.
We provide a brief introduction of Solidity first, then discuss our extension
of behavioral contracts.
We often use \emph{specification} for behavioral contracts to avoid terminological ambiguity.

@@

\begin{lstlisting}
  # ts1 @ f(x) returns z =/> ts2 @ g(a) returns c /\ side-cond
\end{lstlisting}
It enforces that when @g@ is invoked \emph{and} the side condition
evaluates to true, we check that @f@ has not been invoked.

We do not enforce that @g@ cannot be invoked eventually
after invoking @f@.

@@

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "paper"
%%% End:
